---
title: "RMarkdown to Docx: Generic Report"
Author: Novartis
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RMarkdown to Docx: Generic Report}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
# Install and load rdocx
library(rdocx)

# Load other required packages
library(flextable)
library(magrittr)
```

# Introduction

In this vignette we demonstrate using the `rdocx` package for creating a Generic Report Document with the following workflow:

1. The user populates the Rmarkdown template for their report. 
2. The user renders their report as a docx file that follows the style of the provided docx template.
3. The user inspects the docx report and if changes are needed the user can re-generate the report by editing the Rmarkdown template and re-rendering the docx version.

# 1. Populating the Rmarkdown template
For illustrative purposes, a Generic Report Rmd template has been created. In the `rdocx` package, the template is stored here:

`use_cases/01_generic_report/generic_report_template.Rmd`

The template collects the key static elements that are common across all reports as well as examples of some dynamic elements.

If you are new to Rmarkdown then you may find this [cheat sheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf) helpful. 

## Static elements

In the Rmarkdown template the following static elements are supported:

- Title Page
- Change log table
- Signatures table
- Activity table 

Each of these elements are represented as classes in the `rdocx` package. Below is an example of how these are populated in the Rmarkdown template for the title page element. Each attribute of the element has a unique entry that goes through a series of checks once entered. For example, dates are checked to ensure they are in `dd-Mmm-yyyy` format. If the package encounters an unexpected entry the user is alerted through an error message. 

```{r}
# === Provide information for the title page ===
tp <- rdocx::TitlePage$new(
  report_title= "Super cool document",
  department = "Cool department",
  study_title = "Compute super cool things",
  study_number = "OWNDJQW9923",
  status = "Draft",
  version  = "1",
  date = "01-Feb-2024",
  bus_class = "Confidential"
)

```

## Custom elements 

### Tables and Figures

A report can also contain dynamic elements such as tables and figures from your analysis. These can be included by adding your R code that generates these outputs directly to the Rmarkdown file. For example, the following code will create a formatted table using the `flextable` package. 

```{r example-table-vig, out.width='\\textwidth'}
# Generate example data
example_data <- data.frame(
  column_1 = seq(12),
  column_2 = rnorm(12, mean = 10, sd = 1),
  column_3 = paste0(round(rbeta(12, 1, 1), 2)*100, "%")
)
# Make a table
example_data %>%
  flextable::flextable() %>%
  flextable::width(width = 2) %>%
  # Make headers bold
  flextable::bold(bold = TRUE, part = "header") %>%
  # Use zebra theme for row colors
  flextable::theme_zebra() %>%
  # Define column names
  flextable::set_header_labels(
    column_1 = "Header 1",
    column_2 = "Header 2",
    column_3 = "Header 3"
  ) %>%
  # Set borders
  flextable::border_outer() %>%
  flextable::border_inner_h() %>%
  flextable::border_inner_v() %>%
  # Add table captions
  flextable::set_caption(
    caption = "Table 1-2: This is an example table. Add caption text here.",
    style = "Table Caption", autonum = "autonum"
  )
```


### Text
Descriptive text can be added to the Rmarkdown using markdown syntax.

# 2. Rendering your docx file

Now that the Rmarkdown template has been populated with your analysis you can begin the process of rendering your docx file. This process will use the Generic Report Template as the reference document; this document provides the title page structure and the layout style for rendering the docx file. 
Note that the path to the Generic Report Template is configured using the function \code{generic_report_template()}.

If you'd like to get more information on the Generic Report Template version, please call the following function:

```{r}
generic_report_template()
```

Let's render!

```{r,eval=TRUE}
# Template Rmarkdown file that include the details for your sample size report.
rmd_filename <-  system.file(
  "use_cases/01_generic_report/",
  "generic_report_template.Rmd",
   package = "rdocx"
)

# Specify the location where you would like your docx to be written.
# Here we use the same location as the Rmarkdown template.
output_path <- dirname(rmd_filename)

# Define the version (e.g., 0, 1, 12 which will be modified to follow version 
# Numbering guidelines, e.g., _v00, _v01, v_12.) of your report that will be used 
# to name your docx file
version <- 2

rdocx::rmd_render(
  rmd_filename = rmd_filename,
  output_path = output_path,
  version = version
)

```

You should now have rendered your docx file in the location `output_path`. Please review the rendering to ensure it is as expected. 

## Logging your settings and session info

The `rmd_render` function also logs information to aid reproducibility and traceability. The log file will be written to the same location as the `output_path`. The log file will contain the following information:

- The template used

- The name and location of your rendered docx file

- The path from where your R libraries are loaded (i.e. the package bundle version)

- The R session info provided by `sessionInfo()`

👀 If you encounter an error please [raise an issue](ADD LINK) for the {rdocx} package team.
