---
output:
    word_document: 
        toc: yes
toc-title: Table of contents
---


```{r, header, include=F}

# Install rdocx and load it
library(rdocx)

# Load other required R packages 
library(officer)
library(flextable)
library(dplyr)
library(kableExtra)
library(R6)
library(lgr)

# Load R packages for the example plot
library(ggplot2)
library(cowplot)


# These are some examples of commands to set the global options for knitr Rmd compiler. 
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(cache = FALSE)
knitr::opts_chunk$set(tab.cap.pre = "", tab.cap.sep = "")

# Add your custom functions and settings below (if any)

```


```{r, titlepage-info}
# === Provide information for the title page ===

# This information will be displayed on the title page of the rendered
# document.
tp <- TitlePage$new(
  report_title= "Super cool document",
  department = "Cool department",
  study_title = "Compute super cool things",
  study_number = "OWNDJQW9923",
  status = "Draft",
  version  = "1",
  date = "01-Feb-2024",
  bus_class = "Confidential")

```

```{r, changelog-info}
# === Provide information for the change log table ===

# This information will be displayed on the second page of the rendered
# document. You need to add as many ChangelogTableRow elements as rows as you need in your 
# change log table. After that, you'll need to assign these ChangelogTableRow elements
# to a ChangelogTable element.

ctr_1 <- ChangelogTableRow$new(
  date = '01-Oct-2024',
  version = 'Initial version',
  why_update = 'Create first version of the document',
  what_changed = 'NA/ Initial version')

ctr_2 <- ChangelogTableRow$new(
  date = '15-Oct-2024',
  version = 'Final version',
  why_update = 'Change calculation of param 1',
  what_changed = 'Section 2')

changelog_table <- ChangelogTable$new()
changelog_table$add_row(ctr_1)
changelog_table$add_row(ctr_2)

```

```{r}
# === Provide information for the signatures table ===

# This information will be displayed on the third page of the rendered
# document. You need to add as many SignaturesTableRow elements as rows as you need in your 
# signatures table. After that, you'll need to assign these SignaturesTableRow elements
# to a SignaturesTable element.

str <- SignaturesTableRow$new(
  name = 'Harry Styles',
  department = 'eCompliance',
  date = '15-Feb-2024')

str_2 <- SignaturesTableRow$new(
  name = 'Alex Turner',
  department = 'Product Development',
  date = '20-Feb-2024')

signatures_table <- SignaturesTable$new()
signatures_table$add_row(str)
signatures_table$add_row(str_2)


```


```{r, final-title-pages}
# === This code chunk generates the title page (do not modify) ===

# Append change log table and signatures table to the title page
tp$changelog_table <- changelog_table$get_table()
tp$signatures_table <- signatures_table$get_table()
tp$get_title_page()

```

\newpage

# Activity Methodology

&nbsp;

__Introduction__

Start adding your text here. Example text: This document serves as evidence of the accuracy of the information provided in the study protocol OWNDJQW9923 v1 Section X.Y. The calculations and review [or reassessment] were performed by the following statisticians:


```{r statistician-names}
# === Provide information for the Activity Table ===

at <- ActivityTable$new(
  activity = 'Super cool calculation',
  main_author_name = 'David Bowie',
  main_activity_date = '01-Oct-2024',
  qc_author_name = 'Freddie Mercury',
  qc_activity_date = '20-Oct-2024')

at$get_table()
```


&nbsp;
__A table__

You can directly embed tables into this document (see for example Table 1-2).

&nbsp;

```{r example-table, out.width='\\textwidth'}
# === Example Table 1-2 ===

# Generate some example data
example_data <- data.frame(
  column_1 = seq(12),
  column_2 = rnorm(12, mean = 10, sd = 1),
  column_3 = paste0(round(rbeta(12, 1, 1), 2)*100, "%")
)

# Make a table using the {flextable} package
example_data %>%
  flextable::flextable() %>%
  flextable::width(width = 2) %>%
  # Make headers bold
  flextable::bold(bold = TRUE, part = "header") %>%
  # Use zebra theme for row colors
  flextable::theme_zebra() %>%
  # Define column names
  flextable::set_header_labels(
    column_1 = "Header 1",
    column_2 = "Header 2",
    column_3 = "Header 3"
  ) %>%
  # Set borders
  flextable::border_outer() %>%
  flextable::border_inner_h() %>%
  flextable::border_inner_v() %>%
  # Add table captions
  flextable::set_caption(
    caption = "Table 1-2: This is an example table. Add caption text here.",
    style = "Table Caption", autonum = "autonum"
  )
```

&nbsp;
__A figure__

You can also embed figures (see for example Figure 1-1).

```{r example-figure, fig.dim = c(6, 2.5), fig.cap="Figure 1-1: Add your figure caption here.", fig.crop=F}
# === Example Figure 1-1 ===

#   * Adjust figure dimensions using the fig.dim option in the chunk settings 
#     above: fig.dim = (width in inches, length in inches)
#   * Add the figure caption using the fig.cap option in the chunk settings 
#     above: fig.cap = "Add your caption text here".

# Plot ToothGrowth data set using {ggplot2}
ggplot(ToothGrowth) +
  geom_boxplot(
    aes(dose, len, color = supp, group = interaction(dose, supp)),
    width = 0.2,
    outlier.size = 0.5,
    position = position_dodge(width = 0.4)
  ) +
  geom_point(
    aes(dose, len, color = supp),
    position = position_dodge(width = 0.4),
    alpha = 0.7,
    size = 0.5
  ) +
  theme_minimal(base_size = 12) +
  cowplot::panel_border() +
  theme(text = element_text(family = "serif")) + 
  scale_color_brewer(
    name = "Legend title",
    palette = "Dark2"
  ) +
  labs(
    x = "Title x-axis", 
    y = "Title y-axis",
    title = "Example figure"
  )

```

&nbsp;

## This is a subsection 

&nbsp;

You can include subsections, add text here. 

&nbsp;

### This is a subsubsection

&nbsp;

You can also include subsubsection, add text here.

&nbsp;



# References

&nbsp;

Add your references in alphabetical order here (if applicable). For example:

Einstein, A. (1905). On the movement of small particles suspended in a stationary liquid demanded by the molecular-kinetic theory of heat. Theory of Brownian Movement.

# Appendix

## Information for sample size calculation

&nbsp;

Please include additional information as needed.

## Information for sample size verification

&nbsp;

Please include additional information as needed.
